---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Build Status](https://travis-ci.org/johannes-titz/mimosa.svg?branch=master)](https://travis-ci.org/johannes-titz/mimosa)

Mimosa, the mixed models special agent is a shiny app for 2-level mixed models. 

# Installation
No need to install the app, just got to www.mimosa.icu and use it there. An example data file is loaded when you got to www.mimosa.icu/example.

If you really want to use it locally, open R and install the dependencies:

```{r eval = F}
install.packages(c("dplyr", "mlmRev", "lme4", "shiny", "shinyalert",
                   "shinydashboard", "shinyjs", "sjPlot"),
                 repos = "http://cran.us.r-project.org")
```

And now run the app:

```{r echo = T, results = "hide", eval = F}
shiny::runGitHub("mimosa", "johannes-titz")
```

Yes, it is that easy--at least under GNU/Linux! 

If you have any problems installing mimosa, check that your R version is up to date (currently 3.6.1). If you are using Windows, enable TLS 1.2 in the Internet Options Advanced tab (see https://github.com/r-lib/remotes/issues/130#issuecomment-423830669). 

If it still does not work drop me an e-mail at johannes at titz.science or at johannes.titz at gmail.com.

<!-- For an introduction to mimosa please check out [@Titz2020]. -->

# Contributing

Contributions of any kind are very welcome! I will sincerely consider every suggestion on how to improve the internal code and the user interface. Even minor things, such as suggestions for better wording or improving grammar in any part of the package are considered as valuable contributions. If you find any bugs, please use the issue tracker at:

https://github.com/johannes-titz/mimosa/issues

You can also drop me an e-mail and discuss suggestions at: johannes at titz.science or johannes.titz at gmail.com

If you want to make a pull request, please run all tests in the directory *tests* and check that there are no problems. Please also follow the code style described here: http://r-pkgs.had.co.nz/r.html#style

<!-- # References -->